---
title: "Real Time Analysis"
output: html_document
editor_options: 
  chunk_output_type: console
---
Set working directory and load packages.
```{r}
#setwd("~/Dropbox/Tyler")
suppressPackageStartupMessages(library("ggplot2"))
suppressPackageStartupMessages(library("ggmap"))
suppressPackageStartupMessages(library("ggthemes"))
suppressPackageStartupMessages(library("dplyr"))
suppressPackageStartupMessages(library("tidyr"))
suppressPackageStartupMessages(library("rgdal"))
suppressPackageStartupMessages(library("rgeos"))
suppressPackageStartupMessages(library("scales"))
suppressPackageStartupMessages(library("RColorBrewer"))
suppressPackageStartupMessages(library("maps"))
suppressPackageStartupMessages(library("maptools"))
suppressPackageStartupMessages(library("wesanderson"))
suppressPackageStartupMessages(library("sf"))
suppressPackageStartupMessages(library("classInt"))
suppressPackageStartupMessages(library("leaflet"))
suppressPackageStartupMessages(library("Hmisc"))
suppressPackageStartupMessages(library("devtools"))
suppressPackageStartupMessages(library("tidycensus"))
suppressPackageStartupMessages(library("purrr"))
suppressPackageStartupMessages(library("tidyverse"))
suppressPackageStartupMessages(library("MASS"))
suppressPackageStartupMessages(library("tmap"))
suppressPackageStartupMessages(library("tmaptools"))
suppressPackageStartupMessages(library("areal"))
suppressPackageStartupMessages(library("ipumsr"))
```

### Dallas, Texas Tornado (10-20-2019)

```{r}
Dallas = readOGR("Dallas.kml") 

Dallas.sfdf = sf::st_as_sf(Dallas) 
Dallas.sfdf = Dallas.sfdf %>%
  mutate(Name = "Dallas, TX") %>%
  Dallas.sfdf[-c(2)]

tmap_mode("view")
tm_basemap(leaflet::providers$Esri.WorldImagery) +
  tm_tiles("CartoDB.PositronOnlyLabels") +
tm_shape(Dallas.sfdf) +
  tm_polygons(col = "grey", alpha = 0.01, border.col = "red") +
#  tm_shape(AL2010.sf) + 
#  tm_borders(col = "grey80", alpha = 0.3) +
  tm_scale_bar() +
  tm_format_Europe(legend.position = c("left", "bottom"),
                   attr.position = c("left", "bottom"),
                   legend.frame = FALSE) +
  tm_layout(panel.label.bg.color = "white", frame = FALSE)
```

Get Texas 2018 tract data. Only grab total population, total housing units, and mobile home units. Then overlay and extract information about the Dayton, OH tornado.
```{r}
TX2017.sf <- get_acs(state = "TX",
          geography = "tract", 
          variables = c("B01001_001", "B25024_001", "B25024_010"),
          year = 2017,
          output = "wide",
          geometry = TRUE)

TX2017.sf <- st_transform(TX2017.sf, 
                     crs = "+proj=lcc +lat_1=60 +lat_2=30 +lon_0=-90 +units=m")

Dallas.sfdf <- st_transform(Dallas.sfdf, crs = st_crs(TX2017.sf))
Dallas.sfdf$ID <-  1:nrow(Dallas.sfdf)
TX2017.sf$ID2 <- 1:nrow(TX2017.sf)

out2017.sf <- aw_interpolate(Dallas.sfdf, 
               tid = "ID", 
               source = TX2017.sf, 
               sid = "ID2",
               extensive = c("B01001_001E", "B25024_001E", "B25024_010E"),
               weight = "total", 
               output = "sf")
```

The Dallas, TX tornado impacted an estimated 97,250 people. It also impacted an estimate 41,482 housing units and 145 mobile homes.

### Casualty model

To fit the model, first read in indiviudal tornado level estimates. Then edit the information to account for population density, etc.
```{r}
#unzip("SocialCorrelates.zip")
TornSC.sf <- st_read(dsn = "SocialCorrelates", 
                    layer = "SocialCorrelates", 
                    stringsAsFactors = FALSE) %>%
  mutate(date = as.Date(date),
         DateTim = as.POSIXct(paste(yr, mo, dy, time), format = "%Y%m%d%H:%M:%S"))

TornSC.sf$popD = TornSC.sf$TotalPp/TornSC.sf$AreaPth * 10^6
TornSC.sf$PopUnder18 = TornSC.sf$MlUnd18 + TornSC.sf$FmlUn18
TornSC.sf$Pop18to44 = TornSC.sf$Ml18t44 + TornSC.sf$Fml1844
TornSC.sf$Pop45to64 = TornSC.sf$Ml45t64 + TornSC.sf$Fml4564
TornSC.sf$PopOver65 = TornSC.sf$MlOvr65 + TornSC.sf$FmlOv65
```

Create a new data frame with columns containing logged and scaled variables.
```{r}
df <- data.frame(TornSC.sf) %>%
 mutate(lpopD = log(popD),
        lED = log(ED),
        lcas = log(cas),
        lmh = log(MoblHms),
        smi = scale(MdnIncm),
        smh = scale(MoblHms),
        syr = scale(yr),
        pW = White/TotalPp,
        pB = Black/TotalPp)
```

Find the actual path area and popD
```{r}
Dallas.sfdf$PathArea <- st_area(Dallas.sfdf)
Dallas.sfdf$popD <- (out2017.sf$B01001_001E/Dallas.sfdf$PathArea) * 10^6
Dallas.sfdf$mag <- 3
Dallas.sfdf$smh = 2.422507
Dallas.sfdf$syr = 2.05

perc <- c(1, 0, 0, 0, 0, 0, 
         .772, .228, 0, 0, 0, 0,
         .616, .268, .115, 0, 0, 0,
         .529, .271, .133, .067, 0, 0,
         .543, .238, .131, .056, .032, 0,
         .538, .223, .119, .07, .033, .017)
percM <- matrix(perc, ncol = 6, byrow = TRUE)
threshW <- c(29.06, 38.45, 49.62, 60.8, 74.21, 89.41)
midptW <- c(diff(threshW)/2 + threshW[-length(threshW)], threshW[length(threshW)] + 7.5)
ef <- Dallas.sfdf$mag + 1
EW3 <- numeric()
for(i in 1:length(ef)) EW3[i] = midptW^3 %*% percM[ef[i], ]
Dallas.sfdf <- Dallas.sfdf %>%
 mutate(ED = EW3 * PathArea)
```

This is the model.
```{r}
df = df %>%
  dplyr::select(cas, lcas, syr, lpopD, lED, smh, mo, Hour)

df <- df[!is.infinite(rowSums(df)),]

#add dallas data
df2 <- Dallas.sfdf %>%
  mutate(lpopD = log(popD),
         lED = log(ED),
         lmh = log(out2017.sf$B25024_010E),
         mo = 10,
         Hour = 9)

library(lme4)

formula1 <- lcas ~ syr + lpopD + lED + lpopD:lED + smh + (1|mo) + (1|Hour)
m1 <- lmer(formula1, data = df)

summary(m1)
cor(df$cas, exp(predict(m1)))
```

Import code from UDT paper for casualty model (brms).

Work with the **brms** package for mixed effects model. First sample from the priors. Set `inits` to `"0"` rather than the default `"random"`.
```{r}
library(brms)

set.seed(4550)

formula5 <- cas | trunc(lb = 1) ~ syr + lpopD + lED + lpopD:lED + smh + (1|Hour) + (1|mo)
get_prior(formula5, data = df, family = lognormal)
# Sample from the priors
prior5 <- brm(formula = formula5,
              data = df, family = lognormal,
              prior = c(set_prior("normal(0,5)", class = "b"),
                    set_prior("student_t(3, 1, 10)", class = "Intercept"),
                    set_prior("student_t(3, 0, 10)", class = "sd"),
                    set_prior("student_t(3, 0, 10)", class = "sigma")),
          sample_prior = "only", seed = 4550,
          control = list(adapt_delta = .8))
out <- predict(prior5, probs = c(0, 1))
# Fit the model
post5 <- brm(formula = formula5,
             data = df, family = lognormal,
             prior = c(set_prior("normal(0,5)", class = "b"),
                       set_prior("student_t(3, 1, 10)", class = "Intercept"),
                       set_prior("student_t(3, 0, 10)", class = "sd"),
                       set_prior("student_t(3, 0, 10)", class = "sigma")),
              inits = "0", seed = 4520,
              control = list(adapt_delta = .8))
summary(post5)
```

Correlation between estimated and actual casualties.
```{r}
cor(predict(post5)[, 1], df$cas)
```

The `posterior_predict()` function generates 3000 samples of cas. Compare the distribution of cas statistics (mean, max) with actual cas.

```{r}
yrep <- posterior_predict(post5)
df.yrep <- as.data.frame(yrep)
df.out <- reshape2::melt(df.yrep) %>%
  group_by(variable) %>%
  dplyr::summarize(mx = max(value, na.rm = TRUE),
            mn = exp(mean(log(value), na.rm = TRUE)))
quantile(df.out$mn, probs = c(.25, .75), na.rm = TRUE)
quantile(df.out$mx, probs = c(.25, .75), na.rm = TRUE)
```

Look at the posterior predictive checks.
```{r}
ggplot(df.out, aes(mn)) + 
  geom_density(fill = "red", color = "red") +
  geom_vline(xintercept = exp(mean(log(df$cas))), color = "black", size = 1) +
  scale_x_log10(breaks = c(1, 10, 100, 1000), limits = c(1, 1000)) +
  ylab("Posterior Density") +
  xlab("Average Per-Tornado Casualty Rate") +
  theme_minimal()
ggplot(df.out, aes(mx)) + 
  geom_density(fill = "red", color = "red") +
  geom_vline(xintercept = max(df$cas), color = "black", size = 1) +
  scale_x_log10(breaks = c(100, 1000, 10000, 100000), labels = c(100, 1000, 10000, "100,000")) + 
  ylab("Posterior Density") +
  xlab("Maximum Per-Tornado Casualty Rate") +
  theme_minimal()
```

```{r}
coefTable <- as.data.frame(summary(post5)$fixed) %>%
  mutate(lb = `l-95% CI`,
         ub = `u-95% CI`,
         mi = `Estimate`,
         id = 1:6) %>%
  filter(id %in% c(2, 5, 6)) %>%
  mutate(id2 = 1:3)
ggplot(coefTable, aes(x = id2, y = mi)) +
  geom_hline(yintercept = 0, color = "grey", linetype = "solid") +
  geom_hline(yintercept = c(-.6, -.3, .3), color = "grey", linetype = "dashed") +
  geom_point() +  
  geom_errorbar(aes(x = id2, ymin = lb, ymax = ub), col = "red", width = 0, size = 2) +
  geom_point() +
  scale_x_reverse(breaks = 1:3, labels = c("Trend", "Mobile Homes", "Interaction")) +
  ylab("Fixed Effects") + xlab("") +
  theme_minimal() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip() 
```

### Prediction
```{r}
fitted(post5, newdata = df2)
```

