---
title: "Real Time Analysis"
output: html_document
editor_options: 
  chunk_output_type: console
---
Set working directory and load packages.
```{r}
#setwd("~/Dropbox/Tyler")
suppressPackageStartupMessages(library("ggplot2"))
suppressPackageStartupMessages(library("ggmap"))
suppressPackageStartupMessages(library("ggthemes"))
suppressPackageStartupMessages(library("dplyr"))
suppressPackageStartupMessages(library("tidyr"))
suppressPackageStartupMessages(library("rgdal"))
suppressPackageStartupMessages(library("rgeos"))
suppressPackageStartupMessages(library("scales"))
suppressPackageStartupMessages(library("RColorBrewer"))
suppressPackageStartupMessages(library("maps"))
suppressPackageStartupMessages(library("maptools"))
suppressPackageStartupMessages(library("wesanderson"))
suppressPackageStartupMessages(library("sf"))
suppressPackageStartupMessages(library("classInt"))
suppressPackageStartupMessages(library("leaflet"))
suppressPackageStartupMessages(library("Hmisc"))
suppressPackageStartupMessages(library("devtools"))
suppressPackageStartupMessages(library("tidycensus"))
suppressPackageStartupMessages(library("purrr"))
suppressPackageStartupMessages(library("tidyverse"))
suppressPackageStartupMessages(library("MASS"))
suppressPackageStartupMessages(library("tmap"))
suppressPackageStartupMessages(library("tmaptools"))
suppressPackageStartupMessages(library("areal"))
suppressPackageStartupMessages(library("ipumsr"))
```

### Dallas, Texas Tornado (10-20-2019)

```{r}
Dallas = readOGR("Dallas.kml") 

Dallas.sfdf = sf::st_as_sf(Dallas) 
Dallas.sfdf = Dallas.sfdf %>%
  mutate(Name = "Dallas, TX") %>%
  Dallas.sfdf[-c(2)]

tmap_mode("view")
tm_basemap(leaflet::providers$Esri.WorldImagery) +
  tm_tiles("CartoDB.PositronOnlyLabels") +
tm_shape(Dallas.sfdf) +
  tm_polygons(col = "grey", alpha = 0.01, border.col = "red") +
#  tm_shape(AL2010.sf) + 
#  tm_borders(col = "grey80", alpha = 0.3) +
  tm_scale_bar() +
  tm_format_Europe(legend.position = c("left", "bottom"),
                   attr.position = c("left", "bottom"),
                   legend.frame = FALSE) +
  tm_layout(panel.label.bg.color = "white", frame = FALSE)
```

Get Texas 2018 tract data. Only grab total population, total housing units, and mobile home units. Then overlay and extract information about the Dayton, OH tornado.
```{r}
TX2017.sf <- get_acs(state = "TX",
          geography = "tract", 
          variables = c("B01001_001", "B25024_001", "B25024_010"),
          year = 2017,
          output = "wide",
          geometry = TRUE)

TX2017.sf <- st_transform(TX2017.sf, 
                     crs = "+proj=lcc +lat_1=60 +lat_2=30 +lon_0=-90 +units=m")

Dallas.sfdf <- st_transform(Dallas.sfdf, crs = st_crs(TX2017.sf))
Dallas.sfdf$ID <-  1:nrow(Dallas.sfdf)
TX2017.sf$ID2 <- 1:nrow(TX2017.sf)

out2017.sf <- aw_interpolate(Dallas.sfdf, 
               tid = "ID", 
               source = TX2017.sf, 
               sid = "ID2",
               extensive = c("B01001_001E", "B25024_001E", "B25024_010E"),
               weight = "total", 
               output = "sf")
```

The Dallas, TX tornado impacted an estimated 97,250 people. It also impacted an estimate 41,482 housing units and 145 mobile homes.

### Casualty model

Find the actual path area and popD
```{r}
Dallas.sfdf$PathArea <- st_area(Dallas.sfdf)
Dallas.sfdf$popD <- (out2017.sf$B01001_001E/Dallas.sfdf$PathArea) * 10^6
Dallas.sfdf$mag <- 2
Dallas.sfdf$smh = 2.4266140
Beauregard.sfdf$syr = 2.31

perc <- c(1, 0, 0, 0, 0, 0, 
         .772, .228, 0, 0, 0, 0,
         .616, .268, .115, 0, 0, 0,
         .529, .271, .133, .067, 0, 0,
         .543, .238, .131, .056, .032, 0,
         .538, .223, .119, .07, .033, .017)
percM <- matrix(perc, ncol = 6, byrow = TRUE)
threshW <- c(29.06, 38.45, 49.62, 60.8, 74.21, 89.41)
midptW <- c(diff(threshW)/2 + threshW[-length(threshW)], threshW[length(threshW)] + 7.5)
ef <- Beauregard.sfdf$mag + 1
EW3 <- numeric()
for(i in 1:length(ef)) EW3[i] = midptW^3 %*% percM[ef[i], ]
Beauregard.sfdf <- Beauregard.sfdf %>%
 mutate(ED = EW3 * PathArea)
```
The path area of the Beauregard-Smiths Station, AL tornado was 40774487.

```{r}
# Create Dallas tornado data frame

df <- data.frame(pop = )


library(lme4)

formula4 <- lcas ~ syr + lpopD + lED + lpopD:lED + smh + smi + (1|mo) + (1|hr)
m4 <- lmer(formula4, data = df)

summary(m4)
cor(df$cas, exp(predict(m4)))
```
